---
title: "Getting started with binomial package"
author: "Yilin Li"
date: "`r Sys.Date()`"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to binomial package}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---



```{r, echo = FALSE, message = FALSE}
knitr::opts_chunk$set(collapse = T, comment = "#>")
library(binomial)
library(ggplot2)
```

## Binomial

The package `"binomial"` is an implementation for the basic statistics for a random from binomial distribution, and to visualize the relative plots (probability and cumulative distribution).


## Creating a `binvar`

The first step is to create a `"binvar"` object with the function `bin_variable()`:

```{r}
binvar <- bin_variable(10, 0.3)
binvar
```

`bin_variable()` creates a binomial variable with trials and prob as input and its type is the `"binvar"`, that is, a `binomial random variable object.`

The `"binvar"` have 3 methods, like `prinr`,`summary`,`print.summary` where you can check the relaetd statistics (e.g. mean, variance, kurtosis). 
For example, the `summary()` function gives you a nice table of statistics:

```{r}
summary(binvar)
```



## Show the probability

In this package, you can use the function `bin_probablity()` to get the probablity of one or more `success` given number of `trials`. Or the `bin_choose()` to get the number of possible combinations


```{r}
bin_choose(5, 3)
bin_probability(1:5, 10, 0.3)
```


## Plot of relative distributions and cumulatives

The output of `bin_distribution()` will be an object of class 
`"bindis"`, which will contain the data.frame of success number and its corresponding probability with method plot:

```{r}
# plotting binomial probability distribution
dis1 <- bin_distribution(trials = 5, prob = 0.5)
dis1
```
You can use the function `plot()` to create a graphic:

```{r, fig.show='hold'}
plot(dis1)
```

The output of `bin_cumulative()` will be an object of class 
`"bindis"`, which will contain the data.frame of success number and its corresponding probability as well as cumulative probability with method plot:

```{r}
# plotting binomial probability distribution
dis2 <- bin_cumulative(trials = 5, prob = 0.5)
dis2
```
You can use the function `plot()` to create a graphic 

```{r, fig.show='hold'}
plot(dis2)
```
